---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vplotr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

vplotr is a tiny tool for making V-plot matrices ([Henikoff, et. al. 2011](https://www.pnas.org/content/108/45/18318)). It requires a small rust binary which can be found [here](https://github.com/snystrom/vplot).

## Installation

You can install the development version of vplotr using:

``` r
if (!requireNamespace("remotes"))
  install.packages("remotes")

remotes::install_github("snystrom/vplotr")
```

## Example

vplotr only has 1 function: `vplot_matrix` which takes genomic coordinates and
the position of each read midpoint in a bam file, returning a matrix where
columns are genomic coordinates, and rows correspond to the fragment size of the
read (larger fragments are at the top of the matrix).
```{r example, eval=F}
library(vplotr)
library(GenomicRanges)

myRegion <- GRanges("chr3R:16699979-16706691")
vmatrix <- vplot_matrix(myRegion, "path/to/bam.bam")

```

